Sketch Recognition and Understanding

### 2009-08-17 draft/System.tex
adding the matrix

@@

\begin{figure}
	\centering

	\subfigure[First Stroke]{\label{fig:clockstroke1}
		\includegraphics{afterDefense/clockstroke1.jpg.eps} }

		\subfigure[Second Stroke]{	\label{fig:clockstroke2}
		\includegraphics{afterDefense/ClockComplete.jpg.eps}}

		\subfigure[Completed symbol]{
		\label{fig:Clock1}\includegraphics{afterDefense/Clock1.jpg.eps}	}
	\caption{Stroke Drawing Sequence} a) The user first draws the ellipse b) The square wave is drawn inside the ellipse c) The arrows in the symbols illustrate how the user has drawn the symbo
	\label{fig:clock}
\end{figure}

In this step the user draw one or more stroke to draw a symbol. Figure \ref{fig:clock} illustrate the sequence and direction of user draw. In this section, each stroke user draw will be labeled as it illustrated in Figure \ref{fig:clockstroke1} and Figure \ref{fig:clockstroke2} . Table \ref{tab:StepsStroke1} shows the detailed output of the program at each step. The algorithm that compute the segmentation is demonstrated as follows:
\begin{enumerate}

	\item Extracting $P_dp$ as in Section \ref{sec:Preprocessing}
\begin{verbatim*}
  1. For each point in Stroke do the follwoing:
  		1.a Compute distance from previous point.
  		1.b Compute Time difference from previous point and add it to Time_list.  
  		1.c Compute Velocity and add it to Vel_list. (Eq.  ) 
  		1.d Compute Direction and add it to Dir_list.(Eq.  )
  	 	1.e Compute Curvature and add it to Cur_list.(Eq.  ) 
  	end (for loop)
  2. For each  list computed in previous step do the follwing:   (Section )
  	 2.a Compute average of all points. 
  	 2.b set average as threshold.  
  	 2.c Create region from continous points larger than threshold. 
  	 2.d for each region do the following. 
  	 	   2.d.1 find the maximum 
  	 	   2.d.1 Add point to P_dp 
  	  end
     end 
\end{verbatim*}	
\item Ellipse Fitting: which is an attempt to fit as an ellipse as in  Section \ref{sec:EllipseDetection} 
\begin{verbatim*}
1. Initialize the

\end{verbatim*}	
\item Segmentation ALS1 as explained in Section \ref{sec:SwarmSegmentation}
\begin{verbatim*}

\end{verbatim*}	
\item Segmentation ALS2  as explained in Section \ref{sec:PolygonDivisionAlgorithm}
\begin{verbatim*}

\end{verbatim*}

\end{enumerate}

\begin{landscape}
\begin{scriptsize}

%\begin{table}
	%\centering

%\scalebox{0.6}{		
\begin{longtable}{|p{2cm}|p{2cm}|p{2cm}|p{2cm}|p{13cm}|}
\caption{Detailed Output of System in Each Step of Segmentation}
\label{tab:StepsStroke1} \\

@@

 Bonding box is  = Corner P(112.0, 62.0), w= 389.0, h=  316.0
 number of point in this stroke is   62
\end{scriptsize}
 \\ \hline
Possible Dominate point Extraction & Computing and for details see Section\ref{sec:Preprocessing} &  Stroke points  & 1. compute   the pdp  &    Number of $P_{dp}$  = 11
 Pdp = [ 2 (197.0 , 145.0 ), 4 (203.0 , 125.0 ), 3 (198.0 , 140.0 ), 22 (424.0 , 91.0 ), 19 (372.0 , 72.0 ), 26 (492.0 , 164.0 ), 28 (501.0 , 191.0 ), 9 (219.0 , 97.0 ), 31 (496.0 , 239.0 ), 0 (198.0 , 153.0 ), 41 (263.0 , 378.0 )]

@@

@@

\end{landscape}
\subsection{Step by Step Recognition}
\label{sec:steprec}
%\begin{enumerate}
%\begin{itemize}

%	\item Processing for the first Stroke 1.

%	\item Possible Dominiate Point Extraction
%	\item Segmentation 
%	   Computing 
%	\begin{enumerate}
%	\item Ellipse detection  
%	      Calcualting estimated ellipse with radius = $\frac{w}{2}$  and center as same as the bounding box of stroke.  
%	      The ouput of the system $$
% \end{enumerate}
%	
%	
%\end{enumerate}
%  
%
%\end{itemize}

>>>>

 There is mainly two popular methods to change the binary SVM classification problem into Muliclass classification problem. The first methods is One Versus All (OVA) Strategy where M binary classsifiers is constructed one classifier for each class.  The $ith$ classifier is trained using positive example form $ith$ class and negtive example from all other classes. The output function $p_i$ represents the distance and classification of the example from the $ith$ classifier. For a new example $x$, OVA SVM strategy assigns it to the class with the largest value of $p_i$.

 The second method is One Versus One Strategy where a binary classifier for every pair of distinct classes ($M$ classes) and so, all together $\frac{M(M \cdot 1)}{2}$ binary classifiers are constructed. Each binary classifier is trianed using exapmles from both $p_i$ and $p_j$. For example, classifier $C_{ij}$ is trained taking the examples from $p_i$ as positive and the examples from $p_j$ as negative. The classification is based on the number of binary classifer that classifiy the new example as $p_i$. For a new example $x$, if classifier $C_{ij}$ says $x$ is in class $p_i$, then the vote for class $p_i$ is added by one. Otherwise, the vote for class $p_j$  is increased by one. After each of the $\frac{M(M \cdot 1)}{2}$  binary classifiers makes its vote,  OVO strategy assigns $x$ to the class with the largest number of votes.

 Both methods proved to be competitive with each other and there is no clear superiority of one method
over another \cite{Duan05whichis} . Some claims that OVO strategy trains in less time than OVA strategy because they train with only portion of the dataset \cite{libsvm} but this claim have not yet been proofed by expeirments.

@@

\begin{figure}
	\centering
	\subfigure[First Stroke]{\label{fig:clockstroke1}
		\includegraphics[scale=0.7]{afterDefense/clockstroke1.jpg.eps} }

		\subfigure[Second Stroke]{	\label{fig:clockstroke2}
		\includegraphics[scale=0.7]{afterDefense/ClockComplete.jpg.eps}}

		\subfigure[Completed symbol]{
		\label{fig:Clock1}\includegraphics[scale=0.7]{afterDefense/Clock1.jpg.eps}	}
	\caption{Stroke Drawing Sequence} a) The user first draws the ellipse b) The square wave is drawn inside the ellipse c) The arrows in the symbols illustrate how the user has drawn the symbol
	\label{fig:clock}
\end{figure}

In this step the user draw one or more stroke to draw a symbol. Figure \ref{fig:clock} illustrate the sequence and direction of user draw. In this section, each stroke user draw will be labeled as it illustrated in Figure \ref{fig:clockstroke1} and Figure \ref{fig:clockstroke2} . Table \ref{tab:StepsStroke1} shows the detailed output of the program at each step. The input of this step is the stroke points and the ouptut is a list of segments that wil be used in the recognition process. The algorithm that compute the segmentation is demonstrated as follows:
\begin{enumerate}

	\item Extracting $P_dp$ as in Section \ref{sec:Preprocessing}
\begin{verbatim}
  1. For each point in Stroke do the follwoing:
  		1.a Compute distance from previous point.
  		1.b Compute Time difference from previous point and add it to Time_list.  
  		1.c Compute Velocity and add it to Vel_list. 
  		1.d Compute Direction and add it to Dir_list.
  	 	1.e Compute Curvature and add it to Cur_list.(Eq.4.1) 
  	end (for loop)
  2. For each  list computed in previous step do the follwing:   
  	 2.a Compute average of all points. 
  	 2.b set average as threshold.  
  	 2.c Create region from continous points larger than threshold. 
  	 2.d for each region do the following. 
  	 	   2.d.1 find the maximum 
  	 	   2.d.1 Add point to P_dp 
  	  end
     end 
\end{verbatim}	
\item Ellipse Fitting: which is an attempt to fit as an ellipse as in  Section \ref{sec:EllipseDetection} 
%he axes of the ellipse are estimated as the $width/2$ and $height/2$ of the stroke bounding box where $width$ is width and $height$ is height of the bonding box.
\begin{verbatim}
1. Initialize the axes of ellipse  and center by bounding box information
2. Repeat the follwoing for few loops: 
	2.a Compute error in Equation  4.2 
	2.b Update center of ellipse and axis from error. 
3. Compute percent in Equation 4.4 
4. Computer eff in Equation 4.3 
5. if eff < 0.2  then fit as ellipse otherwise move to segment. 
\end{verbatim}

\item Segmentation ALS1 as explained in Section \ref{sec:SwarmSegmentation}. The alogrithm will be similar to the PSO algoirhtm  in section \ref{sec:ParticleSwarmAlgorithm} 
\begin{verbatim}
Initialize 
  1. Generate N particles with M dimensions (P_i...P_N) 
  2. Generate velocities for each particle for M dimension randomly. 
  3. Repeat till Maximum number of iteration OR ErrorThreshold  
         For each particle P_i do the following 
         3.a   Compute fitness  (fitness) 
         				3.a.1 Compute the Error of approximation as in Eq.4.5
         				3.a.2. Computer the fitness function as in Eq. 4.4 
         3.b   Determine Lbest  
               if (lbest_fitness<fitness)
                  3.b.1   lbest=P_i
         3.c      Determine Gbest.
               if (lGest_fitness<fitness)
                  3.c.1   lGest=P_i
         3.d   Compute the Velocity for each dimension using Eq.3.2 
         3.e   Bound Velocity using Eq.3.4
         3.f   Update particle values using Eq. 3.3
         3.g   Refine the location of the particle 
         end .
     end 
4. return Gbest
\end{verbatim}	
\item Segmentation ALS2  as explained in Section \ref{sec:PolygonDivisionAlgorithm}
\begin{verbatim}
Initialize 
  1. Generate N particles with M dimensions (P_i...P_N) 
  2. Generate velocities for each particle for M dimension randomly. 
  3. Repeat till Maximum number of iteration OR ErrorThreshold  
         For each particle P_i do the following 
         3.a   Compute fitness  (fitness) 
              3.a.1 For each Segment in the particle do the following
         				    3.a.1.I   Error of approximation as Line (Eq. 4.7 - 4.9 )
         			      3.a.1.II  Error of approximation as circular arc (Eq. 4.10 - 4.19 )
         				    3.a.1.III Computer minimum of both approximation 
         			3.a.2 Compute Error of the particle as in Eq.  4.20
         			3.a.3 Compute fitness of the particle as in Eq. 4.21
         3.b   Determine Lbest  
               if (lbest_fitness<fitness)
                  3.b.1   lbest=P_i
         3.c      Determine Gbest.
               if (lGest_fitness<fitness)
                  3.c.1   lGest=P_i
         3.d   Compute the Velocity for each dimension using Eq.3.2 
         3.e   Bound Velocity using Eq.3.4
         3.f   Update particle values using Eq. 3.3
         3.g   Refine the location of the particle 
         end .
     end 
4. return Gbest
\end{verbatim}	
\item Append best segmentation to List of segmentation ($L_s$) of this symbols. 
\end{enumerate}

\begin{landscape}
\begin{scriptsize}
%\begin{table}
	%\centering 
%\scalebox{0.6}{		
\begin{longtable}{|p{2cm}|p{2cm}|p{2cm}|p{2cm}|p{13cm}|}
\caption{Detailed Output of System in Each Step of Segmentation}
\label{tab:StepsStroke1} \\

@@

 Bonding box is  = Corner P(112.0, 62.0), w= 389.0, h=  316.0
 number of point in this stroke is   62
\end{scriptsize}
 \\ \hline
Possible Dominate point Extraction & Computing and for details see Section\ref{sec:Preprocessing} &  Stroke points  &   &    Number of $P_{dp}$  = 11
 Pdp = [ 2 (197.0 , 145.0 ), 4 (203.0 , 125.0 ), 3 (198.0 , 140.0 ), 22 (424.0 , 91.0 ), 19 (372.0 , 72.0 ), 26 (492.0 , 164.0 ), 28 (501.0 , 191.0 ), 9 (219.0 , 97.0 ), 31 (496.0 , 239.0 ), 0 (198.0 , 153.0 ), 41 (263.0 , 378.0 )]

@@

  Segmentation & PSO Segmentation ALgS2 & $P_{dp}$  & ALgS2 &   Particles =  [  1 0 1 0 0 1 1 1 1 1 1 0 0 0 1 0 0 0 1 ] 
 The particle  Particles =  [  1 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 1 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 1 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 1 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 1 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 1 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 1 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0 1 0 0 0 0 0 0 1 0 0 0 0 1 0 ]

 Second segmentation PSO = [[[  S0 Line[P(201.0,179.0) to P(195.0,281.0)]  ,      S1 Line[P(195.0,281.0) to P(234.0,304.0)]  ,      S2 Line[P(234.0,304.0) to P(260.0,174.0)]  ,      S3 Line[P(260.0,174.0) to P(325.0,272.0)]  ,      S4 Line[P(325.0,272.0) to P(365.0,304.0)]  ,      S5 Line[P(365.0,304.0) to P(388.0,189.0)]  ,      S6 Line[P(388.0,189.0) to P(431.0,167.0)]  ,      S7 Line[P(431.0,167.0) to P(442.0,220.0)]  ]]]  
 \\ \hline

@@

\end{landscape}
\subsection{Step by Step Recognition}
\label{sec:steprec}

\begin{figure}
	\centering
		\includegraphics{afterDefense/segmentatiofinal.jpg.eps}
	\caption{Best Segmantation }
	\label{fig:segmentatiofinal.jpg}
\end{figure}

%\begin{enumerate}
%\begin{itemize}

	The input of the step is the list of segmentation $L_s$ that is used to computer the feature vector. Figure \ref{fig:segmentatiofinal.jpg} shows the best segmentation as given by the previous step. This step can be summerized as firstly using $L_s$ to computer the feature vector and then introduce this vector the SVM classifier to classify it to one of the trained categories.
